Self Regulation Ontology Retest Data Report

### 2018-02-19 code/SRO_Report.Rmd
updating report w new data

```{r}

```

>>>>

```{r warning=FALSE, message=FALSE}
flat_boot_df <- read.csv(gzfile(paste0(retest_data_path, 'flat_bootstrap_merged.csv.gz')))

hier_boot_df = boot_df[c(boot_df$dv %in% unique(flat_boot_df$dv)),]

flat_boot_df %>%
  select(X, dv, icc) %>%
  left_join(hier_boot_df[,c('X', 'dv', 'icc')], by = c('X', 'dv')) %>%
  group_by(dv) %>%
  do(get_t_test_out(.)) %>%
  mutate(sig_diff = ifelse(p.value<0.05, 1, 0),
         flat_better = ifelse(mean_x>mean_y,1,0)) %>%
  filter(sig_diff == 1)
```
